---
title: "README.md"
author: "Marina FERENT"
date: "2024-10-25"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# tSeriesTools
R package for testing for unit root and stationarizing series.

The package contains functions that:
    (1) test for unit root and display type of non-stationarity based on Ayat and Burridge (2000) sequencial procedure
    (2) based on the exact type of non-stationarity identified, stationarize the series

## Installation
```{r}
library(devtools)
install_github("marinaferent/tSeriesTools")
```

## Usage
```{r}
library(tSeriesTools)
```

**unitRootDF_ABsequential()** - Tests a series for unit root using the Dickey-Fuller test and following the Ayat and Burridge (2000) sequential procedure. It returns a text: A text: "Stationary, no trend", "Stationary around a linear trend", "Random walk with drift", "Unit root and linear trend". 

*Example*
```{r}
library(quantmod)
library(urca)
getSymbols("AAPL", src="yahoo")
unitRootDF_ABsequential(AAPL$AAPL.Close)
unitRootDF_ABsequential(AAPL$AAPL.Close, 0.01)
```

**stationarize()** - Takes a time series of type "Stationary around a linear trend", "Random walk with drift", or "Unit root and linear trend" and returns a time series that is "Stationary, no trend".

*Example*
```{r}
library(quantmod)
library(urca)
getSymbols("AAPL", src="yahoo")
type=unitRootDF_ABsequential(AAPL$AAPL.Close)
aapl_stationary=stationarize(ts(AAPL$AAPL.Close), type=type)
```

**forecastOriginal()** - Takes an ARIMA estimation on stationary and seasonally adjusted series and returns the forecast on the original, non-stationary, not seasonally adjusted series. Currently available only for quarterly data.

*Example*
```{r}
library(urca)
library (forecast)
library(wooldridge)
data('intqrt')
plot(intqrt$r3, type="l")
Tbill3M=ts(as.numeric(intqrt$r3), start=c(1960,1), frequency=4)
Tbill3M_dec=decompose(Tbill3M, type ="multiplicative")
seasonalCoeff=Tbill3M_dec$figure
Tbill3M_sa=ts(Tbill3M/Tbill3M_dec$seasonal, start=c(1960,1), frequency=4)
type=unitRootDF_ABsequential(Tbill3M_sa)
Tbill3M_stationary=stationarize(ts(Tbill3M_sa, start=c(1960,1), frequency=4), type=type)
arimaEstimation=arima(Tbill3M_stationary, order = c(1,0,0))
forecastOriginal(arimaEstimation, type, seasonalCoeff, seasonalityType="multiplicative", nQuarters=8, year=1991, quarter=1, saSeries=Tbill3M_sa)
```

**arimaModelFit()** - Returns the Log likelihood, Akaike information criterion, Bayesian information criterion, Invertible AR roots, and Invertible MA roots of an ARIMA model in an easy to export dataframe.

*Example*
```{r}
library(quantmod)
library(urca)
getSymbols("AAPL", src="yahoo")
type=unitRootDF_ABsequential(AAPL$AAPL.Close)
aapl_stationary=stationarize(ts(AAPL$AAPL.Close), type=type)
arimaEstimation=arima(aapl_stationary, order = c(1,0,0))
arimaModelFit(arimaEstimation, decim=2)
```

